---
title: "HW 4"
output:
  html_document:
    number_sections: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warnings = FALSE, fig.align = 'center',  eval = TRUE)
```

You can run the following code to prepare the analysis.
```{r}
library(r02pro)     #INSTALL IF NECESSARY
library(tidyverse)  #INSTALL IF NECESSARY
library(MASS)
my_sahp <- sahp %>% 
  na.omit() %>%
  mutate(expensive = sale_price > median(sale_price)) %>%
  dplyr::select(gar_car, liv_area, oa_qual, sale_price, 
                expensive) 
my_sahp$expensive <- as.factor(my_sahp$expensive)
```

Please answer the following questions.

1. Use the training data `my_sahp` to fit the following four models of `sale_price`.
- Model 1: linear model on variable `gar_car`.
- Model 2: linear model on variables `gar_car` and `liv_area`.  
- Model 3: KNN with $K=5$ on variables `gar_car` and `liv_area`. 
- Model 4: KNN with $K=50$ on variables `gar_car` and `liv_area`. 

a. Use the validation set approach to divide the data into training (50%) and validation. Compute the average validation error for each model and decide which model is the best.
b. Use LOOCV approach to compute the CV error for each model and decide which model is the best.
c. Use 5-fold CV approach to compute the CV error for each model and decide which model is the best.

2. Use the data `my_sahp` to fit the following four models to predict `expensive`.
- Model 1: logistic regression on variables `gar_car` and `liv_area`.  
- Model 2: LDA on variables `gar_car` and `liv_area`.  
- Model 3: QDA on variables `gar_car` and `liv_area`.  
- Model 4: KNN with $K=20$ on variables `gar_car` and `liv_area`. 

a. Use the validation set approach to divide the data into training (50%) and validation. Compute the average validation classification error for each model and decide which model is the best.
b. Use LOOCV approach to compute the CV classification error for each model and decide which model is the best.
c. Use 5-fold CV approach to compute the CV classification error for each model and decide which model is the best.


3. Q2 from Chapter 5, Page 219, ISLRv2.
