---
title: "HW 6"
author: "Dr. Yang Feng"
output:
  html_document:
    number_sections: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warnings = FALSE, fig.align = 'center',  eval = TRUE)
```

You can run the following code to prepare the analysis.
```{r}
library(r02pro)     #INSTALL IF NECESSARY
library(tidyverse)  #INSTALL IF NECESSARY
library(MASS)
my_ahp <- ahp %>% dplyr::select(gar_car, liv_area, lot_area, oa_qual, sale_price) %>%
  na.omit() %>%
  mutate(type = factor(ifelse(sale_price > median(sale_price), "Expensive", "Cheap")))
tr_ind <- 1:(nrow(my_ahp)/20)
my_ahp_train <- my_ahp[tr_ind, ]
my_ahp_test <- my_ahp[-tr_ind, ]
```

Suppose we want to build a tree to predict `sale_price` and `type`. Please answer the following questions.


1. First, we fit a deep regression tree to predict `sale_price` using the training data `my_ahp_train`. Note that, here we use `tree.control` to generate such a deep tree. 
```{r}
library(tree)
my_control <- tree.control(nrow(my_ahp_train), minsize = 2, mindev = 0)
fit <- tree(sale_price ~ gar_car + liv_area + oa_qual, 
            control = my_control,
            data = my_ahp_train)
```



a.  Prune the tree to different subtrees with the number of terminals nodes ranging from 2 to 20 with increment 1. For each subtree, compute the training error and prediction error on the test data `my_ahp_test`. Visualize the relationship of the two errors vs. the subtree size. 
b. Generate a pruned tree with the number of terminal nodes determined by cross-validation. Then visualize the tree and provide interpretations.  **Note that if many trees have the same cross-validation error, you want to choose the tree with the fewest terminal nodes.**



2. Build a classification tree with the number of terminal nodes determined via cross-validation to predict `expensive` using the training data `my_ahp_train`. Then compute the training and test classification error. 



3. Question 8.4.3 on Page 361 in ISLRv2. 
