---
title: "HW 2"
author: "Dr. Yang Feng"
output:
  word_document: default
  html_document:
    number_sections: yes
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warnings = FALSE, fig.align = 'center',  eval = TRUE)
```

We will be predicting whether the housing price is expensive or not using the `sahp` dataset in the **r02pro** package. 

You can run the following code to prepare the analysis.
```{r}
library(r02pro)     #INSTALL IF NECESSARY
library(tidyverse)  #INSTALL IF NECESSARY
library(MASS)
my_sahp <- sahp %>% 
  na.omit() %>%
  mutate(expensive = sale_price > median(sale_price)) %>%
  dplyr::select(gar_car, liv_area, oa_qual, expensive) 
my_sahp_train <- my_sahp[1:100, ]
my_sahp_test <- my_sahp[-(1:100), ]
```

Please answer the following questions.

1. a. Using the training data `my_sahp_train` to fit a logistic regression model of `expensive` on each variable (`gar_car`, `liv_area`, `oa_qual`) separately. For each logistic regression, compute the training and test error. Which variable leads to the smallest training error? Which variable leads to the smallest test error? 
b. Using the training data `my_sahp_train` to fit a logistic regression model of `expensive` on all three variables (`gar_car`, `liv_area`, `oa_qual`). Compute the training and test error. How do the result compare with part a.

2. Using the training data `my_sahp_train` to fit LDA and QDA models of `expensive` on all three variables (`gar_car`, `liv_area`, `oa_qual`). Compute the training and test error. How do the results compare with Q1? 

3. Q3 in Chapter 4 of ISLRv2. 

4. Q6 in Chapter 4 of ISLRv2. 

