---
title: "Machine Learning in Public Health"
author: "Dr. Yang Feng"
subtitle: 'Lecture 3: Logistic Regression, LDA, QDA (Lab)'
output:
  html_document: 
    number_sections: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warnings = FALSE, fig.align = 'center',  eval = TRUE)
```


The `Default` dataset

```{r, eval=TRUE}
library(tidyverse)
library(ISLR)
attach(Default)
Default[c(1:2,242:244), ]
mytheme <- theme(axis.title = element_text(size = 30),
        axis.text = element_text(size = 20),
        legend.text = element_text(size = 20),
        legend.title = element_text(size = 20))

ggplot(Default) +
  geom_boxplot(mapping = aes(x = default, y = balance)) + 
  mytheme
```

From the boxplots, we guess that `balance` might have good prediction power

# One variable logistic regression

## Use `balance` to predict `default`

- Split the data into training and testing
    ```{r, echo = TRUE}
    default_tr <- Default[1:3000, ]
    default_te <- Default[-(1:3000), ]
    ```

- Fit the logistic regression model on the training data.
    ```{r, echo = TRUE, eval=TRUE,warning=FALSE}
    fit_balance <- glm(default ~ balance, data = default_tr, family='binomial');
    summary(fit_balance)
    ```


## Training Error

- How good is the prediction on training data?
    ```{r, echo=TRUE, eval=TRUE, warning=FALSE, fig.asp=0.45}
    pred_train_prob <- predict(fit_balance, type = 'response')
    pred_train_label <- ifelse(pred_train_prob > 0.5, 'Yes', 'No')
    table(pred_train_label, default_tr$default) #Confusion Table
    ```

- Now, we can get the training error.
    ```{r,echo=TRUE,eval=TRUE,warning=FALSE,fig.asp=0.45}
    mean(pred_train_label != default_tr$default)
    ```


- The overall training classification error looks good.


## Test Error

- How good is the prediction on test data?
    ```{r, echo=TRUE, eval=TRUE, warning=FALSE, fig.asp=0.45}
    pred_test_prob <- predict(fit_balance, newdata = default_te, type = 'response')
    pred_test_label <- ifelse(pred_test_prob > 0.5, 'Yes', 'No')
    table(pred_test_label, default_te$default)
    ```

- Now, we can get the test classification error.
    ```{r,echo=TRUE,eval=TRUE,warning=FALSE,fig.asp=0.45}
    mean(pred_test_label != default_te$default)
    ```


- The overall test classification error looks also very good!


# Multiple logistic regression


## Predict `default` using both `balance` and `student`:

    ```{r,echo=TRUE,eval=TRUE,warning=FALSE,fig.asp=0.45}
    fit_bal_stu <- glm(default ~ balance + student, data= default_tr, family='binomial')
    ```

```{r,echo=TRUE,eval=TRUE,warning=FALSE,fig.asp=0.45}
summary(fit_bal_stu)
```

## (Multiple) logistic regression: compute the training error

```{r,echo=TRUE,eval=TRUE,warning=FALSE,fig.asp=0.45}
pred_train_prob <- predict(fit_bal_stu, type = 'response')
pred_train_label <- ifelse(pred_train_prob > 0.5, 'Yes', 'No')
table(pred_train_label, default_tr$default)
mean(pred_train_label != default_tr$default)
```


- This training classification error is smaller than that of the model using just `balance`


##  (Multiple) logistic regression: compute the test error

```{r,echo=TRUE,eval=TRUE,warning=FALSE,fig.asp=0.45}
pred_test_prob <- predict(fit_bal_stu, newdata = default_te, type = 'response')
pred_test_label <- ifelse(pred_test_prob > 0.5, 'Yes', 'No')
mean(pred_test_label != default_te$default)
```

- The same error as only using the `balance`.

# Linear Discriminant Analysis (LDA)
## Analyzing Default Data using LDA


```{r,echo=TRUE,eval=TRUE,warning=FALSE,fig.asp=0.45}
library(MASS) # lda() is in `MASS` library
lda.fit <- lda(default ~ balance, data = default_tr)
lda.fit
```


## Training and Test Error

- Training Error
    ```{r,echo=TRUE,eval=TRUE,warning=FALSE,fig.asp=0.45}
    lda.predict <- predict(lda.fit, default_tr)
    lda.class <- lda.predict$class
    mean(lda.class != default_tr$default)
    ```


- Test Error
    ```{r, echo=TRUE}
    lda.predict <- predict(lda.fit, default_te)
    lda.class <- lda.predict$class
    mean(lda.class != default_te$default)
    ```

# Quadratic discriminant analysis (QDA)

## Analyzing Default Data using QDA


```{r,echo=TRUE,eval=TRUE,warning=FALSE,fig.asp=0.45}
qda.fit <- qda(default ~ balance, data = default_tr)
qda.fit
```


## Training and Test Error

- Training Error
    ```{r,echo=TRUE,eval=TRUE,warning=FALSE,fig.asp=0.45}
    qda.predict <- predict(qda.fit, default_tr)
    qda.class <- qda.predict$class
    mean(qda.class != default_tr$default)
    ```


- Test Error
    ```{r, echo=TRUE}
    qda.predict <- predict(qda.fit, default_te)
    qda.class <- qda.predict$class
    mean(qda.class != default_te$default)
    ```


