---
title: "Machine Learning in Public Health"
author: "Dr. Yang Feng"
subtitle: 'Lecture 7: Regression and Classification Trees (Lab)'
output:
  html_document: 
    df_print: paged
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warnings = FALSE, fig.align = 'center',  eval = TRUE, out.width = "70%")
```

# Predicting a baseball player’s Salary

Using the Hitters data set. Based on Years (the number of years that he has played in the major leagues) and Hits (the number of hits that he made in the previous year). 
```{r}
library(tidyverse)
data(Hitters, package = 'ISLR')
salary <- Hitters %>% 
  select(Salary, Years, Hits) %>%
  drop_na() %>%
  mutate(logSalary = log(Salary))
```

The first few rows of the data
```{r}
head(salary)
```


## Fit a Decision Tree

```{r}
library(tree)
sal.tree <- tree(logSalary ~ Years + Hits, data = salary)
plot(sal.tree)
text(sal.tree)
```

## Pruning the tree

```{r}
sal.tree.prune <- prune.tree(sal.tree, best = 2) #The subtree with two terminal nodes
plot(sal.tree.prune)
text(sal.tree.prune)
```



```{r}
sal.tree.prune <- prune.tree(sal.tree, best = 3) #The subtree with three terminal nodes
plot(sal.tree.prune)
text(sal.tree.prune)
```





## Cross-validation to predict the log Salary

```{r}
sal.tree <- tree(logSalary ~ Years + Hits, data = salary)
set.seed(0)
cv.sal <- cv.tree(sal.tree)
#names(cv.sal)
cv.sal_df <- data.frame(size = cv.sal$size, deviance = cv.sal$dev)
best_size <- cv.sal$size[which.min(cv.sal$dev)]
ggplot(cv.sal_df, mapping = aes(x = size, y = deviance)) + 
  geom_point(size = 3) + 
  geom_line() +
  geom_vline(xintercept = best_size, col = "red")
#cat('CV leads to the optimal tree size as ', best_size,'\n')
```

## Visualizing the pruned regression tree

```{r}
sal.tree.final <- prune.tree(sal.tree, best = best_size) #The subtree with best_size terminal nodes
plot(sal.tree.final)
text(sal.tree.final)
```

## Computer the training error
```{r}
pred_salary <- predict(sal.tree.final, newdata = salary)
mean((pred_salary - salary$logSalary)^2)
```


# Trees for classification 

## Example for predicting high salary

Create `salary <- salary %>% mutate(high_salary = logSalary > median(logSalary))`.
```{r}
salary <- salary %>% mutate(high_salary = logSalary > median(logSalary))
salary$high_salary <- as.factor(salary$high_salary)
sal.tree <- tree(high_salary ~ Years + Hits, data = salary)
set.seed(0)
cv.sal <- cv.tree(sal.tree)
#names(cv.sal)
cv.sal_df <- data.frame(size = cv.sal$size, deviance = cv.sal$dev)
best_size <- cv.sal$size[which.min(cv.sal$dev)]
ggplot(cv.sal_df, mapping = aes(x = size, y = deviance)) + 
  geom_point(size = 3) + 
  geom_line() +
  geom_vline(xintercept = best_size, col = "red")
```

## Visualizing the pruned classification tree

```{r}
#cat('CV leads to the optimal tree size as ', best_size,'\n')
sal.tree.final <- prune.tree(sal.tree, best = best_size) #The subtree with best_size terminal nodes
plot(sal.tree.final)
text(sal.tree.final)
```


## Using the Gini criterion to split

```{r}
salary <- salary %>% mutate(high_salary = logSalary > median(logSalary))
salary$high_salary <- as.factor(salary$high_salary)
sal.tree <- tree(high_salary ~ Years + Hits, data = salary, split = "gini")
set.seed(0)
cv.sal <- cv.tree(sal.tree)
#names(cv.sal)
cv.sal_df <- data.frame(size = cv.sal$size, deviance = cv.sal$dev)
best_size <- cv.sal$size[which.min(cv.sal$dev)]
ggplot(cv.sal_df, mapping = aes(x = size, y = deviance)) + 
  geom_point(size = 3) + 
  geom_line() +
  geom_vline(xintercept = best_size, col = "red")
```

## Visualizing the pruned classification tree

```{r}
#cat('CV leads to the optimal tree size as ', best_size,'\n')
sal.tree.final <- prune.tree(sal.tree, best = best_size) #The subtree with best_size terminal nodes
plot(sal.tree.final)
text(sal.tree.final)
```



## Computer the training classification error
```{r}
pred_high_salary <- predict(sal.tree.final, newdata = salary, type = "class")
mean(pred_high_salary != salary$high_salary)
```



