---
title: "Lecture 9: PCA (Lab)"
output:
  html_document:
  df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```



## PCA

We will use the `USArrests` dataset.
```{r}
library(ISLR)
states <- row.names(USArrests)
apply(USArrests, 2, mean)
apply(USArrests, 2, var)
```

Compute the PCA
```{r}
pr.out <- prcomp(USArrests, scale = TRUE)
names(pr.out)
```

The standard deviations of the principal components (i.e., the square roots of the eigenvalues of the covariance/correlation matrix).
```{r}
pr.out$sdev
```

The centering and scales used:
```{r}
pr.out$center
pr.out$scale
```


The matrix of variable loadings (i.e., a matrix whose columns contain the eigenvectors).
```{r}
pr.out$rotation
```


Create a biplot:
```{r}
biplot(pr.out, scale = 0)
```

Compute the Percentage of Variance Explained (PVE):
```{r}
pr.var <- pr.out$sdev^2
pve <- pr.var / sum(pr.var)
pve
```

Visualization:
```{r}
par(mfrow = c(1, 2))
plot(pve, xlab = "Principal Component",
ylab = "Proportion of Variance Explained", ylim = c(0, 1),
type = "b")
plot(cumsum(pve), xlab = "Principal Component",
ylab = "Cumulative Proportion of Variance Explained", ylim = c(0, 1), type = "b")
```

## Doing PCA without the function

```{r}
my_cor <- cor(USArrests)
my_scale <- scale(USArrests)
attr(my_scale, "scaled:center")
attr(my_scale, "scaled:scale")
my_cor_eigen <- eigen(my_cor)
sqrt(my_cor_eigen$values)
my_cor_eigen$vectors
```

