---
title: "KNN Regression"
output: 
  learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(r02pro)
library(tidyverse)
```

We will be predicting the housing price using the `sahp` dataset in the **r02pro** package. Please answer the following questions.

You can run the following code to prepare the analysis.
```{r}
my_sahp <- sahp %>% 
  na.omit() %>%
  select(gar_car, liv_area, kit_qual, sale_price)
my_sahp_train <- my_sahp[1:100, ]
my_sahp_test <- my_sahp[-(1:100), ]

head(my_sahp)
```

Now, use the KNN method for predicting the `sale_price` using all predictors. 
    Vary the nearest number $K$ from 1 to 50 with increment 1. For each $K$, fit the KNN regression model on the training data, and predict on the test data. Visualize the training and test error trend as a function of $K$. Discuss your findings.

```{r simpleLRQ3, exercise = TRUE}

```

```{r simpleLRQ3-solution}
library(caret)
k_seq <- seq(from = 1, to = 50, by = 1)
train_error_seq <- test_error_seq <- NULL
for(k_ind in seq_along(k_seq)){
  k <- k_seq[k_ind]
knn_fit <- knnreg(sale_price ~ ., 
                  data = my_sahp_train,
                  k = k)
sale_price_pred <- predict(knn_fit, newdata = my_sahp_train)
  train_error_seq[k_ind] <- sum((my_sahp_train$sale_price - sale_price_pred)^2)
  sale_price_pred <- predict(knn_fit, newdata = my_sahp_test)
  test_error_seq[k_ind] <- sum((my_sahp_test$sale_price - sale_price_pred)^2)
  
}
re <- rbind(data.frame(k = k_seq, error = train_error_seq, type = "train"),
            data.frame(k = k_seq, error = test_error_seq, type = "test"))
                      
ggplot(re, mapping = aes(x = k, y = error, color = type)) +
  geom_line() +
  geom_point()
k_best <- k_seq[which.min(test_error_seq)]
test_error_seq[k_best]

```
