---
title: "Logistic Regression"
output: 
  learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(r02pro)
library(tidyverse)
library(MASS)
```

We will be predicting whether the housing price is expensive or not using the `sahp` dataset in the **r02pro** package. 

You can run the following code to prepare the analysis.
```{r}
my_sahp <- sahp %>% 
  na.omit() %>%
  mutate(expensive = sale_price > median(sale_price)) %>%
  dplyr::select(gar_car, liv_area, oa_qual, expensive) 
my_sahp_train <- my_sahp[1:100, ]
my_sahp_test <- my_sahp[-(1:100), ]

head(my_sahp)
```

Please answer the following questions.

# Question 1

Using the training data `my_sahp_train` to fit a logistic regression model of `expensive` on each variable (`gar_car`, `liv_area`, `oa_qual`) separately. For each logistic regression, compute the training and test error. Which variable leads to the smallest training error? Which variable leads to the smallest test error? 

```{r LogregQ1, exercise = TRUE}

```


# Question 2

Using the training data `my_sahp_train` to fit a logistic regression model of `expensive` on all three variables (`gar_car`, `liv_area`, `oa_qual`). Compute the training and test error. How do the result compare with question 1.

```{r LogregQ2, exercise = TRUE}

```

```{r LogregQ2-solution}
vars <- c("gar_car", "liv_area", "oa_qual")
train_error_seq <- test_error_seq <- NULL
re <- NULL
beta_coef_seq <- NULL
for(var_ind in seq_along(vars)){
  var <- vars[var_ind]
  dat <- my_sahp_train %>% dplyr::select(expensive, all_of(var))
  fit <- glm(expensive ~., data = dat, family = "binomial")
  print(coef(fit))
  expensice_pred <- predict(fit, newdata = my_sahp_train)
  train_error_seq[var_ind] <- mean(my_sahp_train$expensive != (expensice_pred > 0.5))
  expensice_pred <- predict(fit, newdata = my_sahp_test)
  test_error_seq[var_ind] <- mean(my_sahp_test$expensive != (expensice_pred > 0.5))
}
 
fit_all <- glm(expensive ~ ., data = my_sahp_train, family = "binomial")
print(coef(fit_all))
expensice_pred_all <- predict(fit_all, newdata = my_sahp_train)
train_error_seq_all <- mean(my_sahp_train$expensive != (expensice_pred_all > 0.5))
expensice_pred_all <- predict(fit_all, newdata = my_sahp_test)
test_error_seq_all <- mean(my_sahp_test$expensive != (expensice_pred_all > 0.5))

 glm_re <- data.frame(var = c(vars, "all"),
                  train_error = c(train_error_seq, train_error_seq_all),
                  test_error = c(test_error_seq, test_error_seq_all))
 glm_re
```