---
title: "Multiple Linear Regression"
output: 
  learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(r02pro)
library(tidyverse)
```

We will be predicting the housing price using the `sahp` dataset in the **r02pro** package. Please answer the following questions.

You can run the following code to prepare the analysis.
```{r}
my_sahp <- sahp %>% 
  na.omit() %>%
  select(gar_car, liv_area, kit_qual, sale_price)
my_sahp_train <- my_sahp[1:100, ]
my_sahp_test <- my_sahp[-(1:100), ]

head(my_sahp)
```


Using the training data `my_sahp_train` to fit a linear regression model of `sale_price` on all variables, interpret the coefficients and compute the $R^2$. Then compute the training and test error. Compare the results to Q1 and explain your findings.

```{r simpleLRQ2, exercise = TRUE}

```

```{r simpleLRQ2-solution}
fit_all <- lm(sale_price ~., data = my_sahp_train)
summary(fit_all)
 sale_price_pred <- predict(fit_all, newdata = my_sahp_train)
  train_error_seq <- c(train_error_seq, sum((my_sahp_train$sale_price - sale_price_pred)^2))
  sale_price_pred <- predict(fit_all, newdata = my_sahp_test)
  test_error_seq <- c(test_error_seq, sum((my_sahp_test$sale_price - sale_price_pred)^2))
  R2_seq <- c(R2_seq, summary(fit_all)$r.squared)
  vars <- c(vars, "All")
  lm_re <- data.frame(var = vars,
                         R2 = R2_seq,
                        train_error = train_error_seq,
                        test_error = test_error_seq)
 lm_re
```