---
title: "HW 9"
author: "Dr. Yang Feng"
output:
  html_document:
    number_sections: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warnings = FALSE, fig.align = 'center',  eval = TRUE)
```


You can run the following code to prepare the analysis.
```{r}
library(r02pro)     #INSTALL IF NECESSARY
library(tidyverse)  #INSTALL IF NECESSARY
library(MASS)
my_ahp <- ahp %>% dplyr::select(gar_car, liv_area, lot_area, bsmt_area, gar_area, oa_qual, sale_price, bedroom, bathroom, yr_built) %>%
  na.omit()
my_ahp_x <- my_ahp %>% dplyr::select(-sale_price)
my_ahp_y <- my_ahp %>% dplyr::select(sale_price)
```

1. Conduct PCA on `my_ahp_x` with `scale = TRUE`. 
a. Create a biplot. 
b. Plot the Proportion of Variance Explained and the Cumulative Proportion of Variance Explained. 
c. Fit a linear regression of `sale_price` on the first two principle components. What's the $R^2$? 
d. Fit a linear regression of `sale_price` on `gar_car` and `liv_area`. What's the $R^2$? 

2. Conduct PCA on `my_ahp_x` with `scale = FALSE` and compare the results of a-c with those of Q1. 
a. Create a biplot. 
b. Plot the Proportion of Variance Explained and the Cumulative Proportion of Variance Explained. 
c. Fit a linear regression of `sale_price` on the first two principle components. What's the $R^2$? 

