---
title: "HW 3"
author: "Dr. Yang Feng"
output:
  pdf_document: default
  html_document:
    number_sections: yes
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warnings = FALSE, fig.align = 'center',  eval = TRUE)
```

We will be predicting whether the housing price is expensive or not using the `sahp` dataset in the **r02pro** package. 

You can run the following code to prepare the analysis.
```{r}
library(r02pro)     #INSTALL IF NECESSARY
library(tidyverse)  #INSTALL IF NECESSARY
library(MASS)
my_sahp <- sahp %>% 
  na.omit() %>%
  mutate(expensive = sale_price > median(sale_price)) %>%
  dplyr::select(gar_car, liv_area, oa_qual, expensive) 
my_sahp$expensive <- as.factor(my_sahp$expensive)
my_sahp_train <- my_sahp[1:100, ]
my_sahp_test <- my_sahp[-(1:100), ]
```

Please answer the following questions.

1. Use the training data `my_sahp_train` to fit a KNN model of `expensive` on variables `gar_car` and `liv_area`.  

a. Vary the nearest number $K$ from 1 to 100 with increment 5. For each $K$, fit the KNN classification model on the training data, and predict on the test data. Visualize the training and test error trend as a function of $K$. Discuss your findings.

b. First, standardize `gar_car` and `liv_area`. Then, repeat the task in a, and visualize the training and test error together with the unstandarized version as a function of $K$.


2. Use the data `my_sahp` (without standardization) to fit four models of `expensive` on variables `gar_car` and `liv_area`, using Logistic regression, LDA, QDA, and KNN (with $K = 7$). Visualize the ROC curves for them and add the AUC values to the legend. Discuss your findings.


3. ISLRv2 Chapter 4 Q4